\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\usepackage{geometry}
\usepackage{array}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{siunitx}

\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

\title{CSE 308 July 2015 Weekly Schedule for Subsection B2}

\author{Khaled Mahmud Shahriar, Tanvir Ahmed Khan}

\date{\today}

\begin{document}

\maketitle

\renewcommand{\arraystretch}{1.3}
\begin{center}
    \begin{tabular}{|>{\centering\arraybackslash}m{0.08\textwidth}|>{\centering\arraybackslash}m{0.3\textwidth}|>{\centering\arraybackslash}m{0.35\textwidth}|>{\centering\arraybackslash}m{0.15\textwidth}|}
    \hline
    \textbf{Week} & \textbf{Student's Assignment} & \textbf{Demonstration} & \textbf{Presentation}\\
    \hline
    6 & \textbf{Requirement Analysis} & Introduction to MVC framework \& Software Prototyping & \xmark\\
    \hline
    7 & \textbf{Use-case} Diagram & Design Patterns by Example & \SI{15}{minutes}\\
    \hline
    8 & \textbf{Online} on Design Pattern & \xmark & \xmark\\
    \hline
    9 & \textbf{Prototype} Presentation & Introduction to Unit Testing with \texttt{JUnit} & \SI{15}{minutes}\\
    \hline
    10 & \textbf{Class} \& \textbf{Collaboration} Diagrams & Introduction to Version Control System with \texttt{git} & \SI{15}{minutes}\\
    \hline
    11 & \textbf{Sequence} \& \textbf{State} Diagrams & \xmark & \SI{15}{minutes}\\
    \hline
    12 & \textbf{Full Project Presentation} & \xmark & \SI{20}{minutes}\\
    \hline
    \end{tabular}
\end{center}
Students will analyze the requirement of the software throughout the week 5-7. They will study the existing system, talk with the system users, learn what are their requirements for the software, and collect all the necessary information within this time. Students will submit their update on requirement analysis and teachers will give their feedback on week 6. Based on these feedback, students will study the system further and present the use-case diagram of the system on week 7. From these use-cases students will start developing the software. The first prototype of the software will be presented in the next class, week 9. As the student will start developing the software, the update of their development will be presented in the form of class, collaboration, sequence, and state diagram throughout the week 10 and 11. The final project will then be presented on week 12.

\iffalse
Few guidelines are-
\begin{itemize}
 \item For use-case diagram, show use-cases for exactly two subsystems. For use-case description, present exactly three use-cases. You should create use-cases for other subsystems as well but you don't have to present them in your presentation.
 \item For prototype design, design the various screens of your software using standard prototyping softwares.
\end{itemize}
\fi
\end{document}
